\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-06-22 doc/USER_MANUAL/01_introduction.tex
switched the license to GNU version 3 (now that we use pyCMT3D, which is LGPL v3, the combination automatically becomes GNU version 3). Also added FWI inversion information to the users manual.

\red{\Large ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-)}\\

>>>>

\red{\Large ANNOUNCEMENT: SPECFEM3D can now perform full waveform inversion (FWI), i.e. invert for models in an iterative fashion, and it can also perform source inversions in a constant model;
please refer to the two new directories, \texttt{inverse\_problem\_for\_model} and \texttt{inverse\_problem\_for\_source}, and the README files they contain. For FWI inversions for the model, also refer to the new examples provided in
directory \texttt{EXAMPLES}.}\\

\red{OTHER ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-)}\\
